Field-informed Reinforcement Learning of Collective Tasks with Graph Neural Networks

### 2023-05-20 paper.tex
3A title
chore: discuss about computational field and gnn

  Therefore, this graph can be used for being processed by a \ac{GNN} as done in~\cite{DBLP:conf/corl/TolstayaGPP0R19,tolstaya2020learning,DBLP:conf/icra/GosrichMLPYR022} if we set $f_v = o^v_t$.

@@

\subsection{Architecture and System dynamics}

>>>>

  This graph can be used both to compute computational fields and as input for a GNN, as done in previous work~\cite{DBLP:conf/corl/TolstayaGPP0R19,tolstaya2020learning,DBLP:conf/icra/GosrichMLPYR022}.
  % if we set $f_v = o^v_t$.

@@

\subsection{Architecture, fields and aggregate dynamics}
